\documentclass[char]{Emperia}
\begin{document}
\name{\cJester{}}

You made a\ldots{} deal. A deal with the powers that be, quite literally. They call themselves Gods, and, compared to the sleepers in this world, they might as well be. 

Luckily, you're not one of them.

You are not quite sure what you are, but you do know that you've been hopping dimensions for a Very Long Time. 214 years ago, you hopped from <insert thing here> to this place - where the unique magics trapped you. 214 years ago, you were a hero. You went on epic quests and eventually defeated an ancient red dragon. The next morning, you woke up as someone new, two countries away. 150 years ago, you became an apprentice mage and worked your way up to archmage. 50 years ago, you were born a pauper, and through luck and chance became a \monarch{}. For the last 12 years, you have been a humble Jester. 

It's taken you a little while to work out how to escape this world, but by this point, you know that the answer lies in the poor mortal saps around you. You need to harness the power of a court full of fully awakened individuals to catapult you out of this accursed dimension. 

Alas, awakening is not a thing easily achieved. The ``Gods'' forbid it under normal circumstances. You are quite proud of the clever 



TODO
Specify what the deal was - got the gods to sit down and talk to the jester. The gods are bored out of their skulls - after all, what is a jester for but to provide amusement. The gods have agreed to awaken a single person and see where that takes the court, with a time limit of 2 hours. After which, everything would go back to normal. But that should be ample time for you to affect your escape.


You should preserve the integrity of the story by not drawing attention to yourself as an extra-dimensional being. As such, don't reveal your powers to awaken at will if at all possible.


\end{document}
