\documentclass[blue]{Emperia}
\begin{document}
\name{\bNeutralReligion{}}

%For Druid and Jester
%%Explain ancient conflict (since man was created)
%Galadin = L/C; Elph = G/E; list 2 atrocities and 1 miracle; Churches focus on the "good" aspects, ignore the "bad".

In the country of Emperia, there are two religions. One worships \cGaladin{}, \cGaladin{\God} of Renewal. The other worships \cElph{}, \cElph{\God} of Virtue. The two churches, and the conflict between them, have existed since time immemorial. Most citizens subscribe to one or other church, with a silent minority subscribing to neither. 

\section{The Church of Renewal}
The Church of Renewal believes in the divinity of renewal, change, and, paradoxically, tradition. They worship \CGaladin{} as the one true \cGaladin{\God}, and hold to \CGaladin{\their} teachings. Unlike \cElph{}, \cGaladin{} supposedly sent down commandments for \CGaladin{\their} followers, giving them much needed direction in the tumultuous times of the early ages of humanity. For purely academic interests, the commandments are as follows: 

\begin{enumerate}
\item Do not allow your life to stagnate. Embrace change.
\item Challenge others in unexpected ways.
\item Question authority but bow to tradition.
\item Complexity and nuance enrich life.
\item Enforce order.
\end{enumerage}

\CGaladin{} is also credited with creating the seasons out of a previously endless summer. If this is true, \cGaladin{} allowed for a much wider variety of life to thrive across the world, at the cost of easy crops year round, and the dangerous, deadly winters of \pEmperia{}.

Even more controversial is \cGaladin{}'s recent divine act of turning an entire village into a herd of Centaur. While the Church of Renewal brands this as a ```miracle'', noting the change, new life, and new capabilities of the townsfolk, an opposing view of the matter says that the personalities of the villagers were all but wiped out by their change, effectively meaning that this was a disguised massacre - or so says the Church of Virtue.

\section{Church of Virtue}
The Church of Virtue believes that good and evil are absolutes. Their god is \cElph{}, and they follow \cElph{\them} with a fervor bordering on fanaticism.

\cElph{}'s most recent miracle was handing down the divine right to rule to the \cMonarch{}'s grand\cMonarch{\parent}, over the body of the dictator, Robin the Red. Robin the Red had waged a war of conquest against \pEmperia{} starting 6 years ago, and had been peacefully in power for the last 2 of those years. Robin the Red, while hated by the populace for their lost kin, was a fairly benevolent dictator once the dust had settled. But without warning, \cElph{} scoured the palace with fire, immolating everyone within - everyone, that is, except for the gardener, who \cElph{} protected with a column of divine light. The light carried the gardener high above the palace, so that everyone could see the favor of the gods. Then the God returned them safely to the ground, clad in finery befitting a Monarch, made of a material not of this world, bearing the emblem of \cElph{}. That was \cMonarch{}'s grand\cMonarch{\parent}, who was from that point on, the ruler of \pEmperia{}.

The Church of Virtue was ecstatic about this. Their god had divinely appointed a ruler who went on to be benevolent and kind. The Church of Renewal, however, was more dubious, especially once their heir turned out to be a lazy, self-centered alcoholic. As far as history is concerned, the change in management may have pleased the people, but was essentially neutral for the health of \cEmperia{}.

The most dramatic of \cElph{}'s ```miracles''.


/\



EVIL: super harsh punishment for someone(s) - Wiping a country off the map (sink the entire continent?) A mad king goes on a rampage, ignoring warnings from Elph who eventually sinks the whole continent, killing good and evil.

\end{document}
